Finding Optimal Sequences for Area Aggregation---\protect\\ \Astar vs. Integer Linear Programming

### 2019-03-17 area_agg_seq_tsas.tex
addressed the comments from TSAS

In each step of the sequence that we compute, 
the smallest area is merged with one of its neighbors. 
We do not select that neighbor according to a prescribed rule 
but compute the whole sequence of pairwise merges at once, 
based on global optimization.
We formalize this optimization problem as that of 
finding a shortest path in a (very large) graph.
We present the \Astar algorithm and integer linear programming
to solve this optimization problem.
To avoid long computing times, we allow the two methods to 
return non-optimal results.
In addition, we present a greedy algorithm as a benchmark.
We tested the three methods with a
dataset of the official German topographic database ATKIS.
Our main result is that
\Astar finds optimal aggregation sequences for more instances 
than the other two methods
within a given time frame.
%
%
\end{abstract}

@@

In our digital age, people interactively read maps 
on computers and mobile phones.
An often used interaction is zooming. 
When users zoom in or out, 
a map must be changed to provide information 
appropriate to the corresponding zoom level.
However, large discrete changes may distract users.
The \emph{on-the-fly generalization}~\parencite{Weibel2017Fly},
which generalizes features in real time, can mitigate this problem.
Still, large discrete changes can be introduced.
By a usability test, \textcite{Midtbo2007} have shown that 
a map is easier to follow 
if the map extent transits smoothly than stepwise. 
In addition to smoothly transiting map extent, 
we want to change also map features smoothly 
when users are zooming.
we believe that this strategy will allow users 
to follow maps even more easily.
The process of producing maps at any different scales
with smooth changes 
is known as \emph{continuous map generalization} (CMG), 
or simply \emph{continuous generalization}.
Ideally, there should be no discrete change in CMG.
However, the term is also used when 
the discrete changes are small enough not to be noticed as,
e.g., \textcite{Suba2016Road} state.

CMG has received a lot of attention
from cartographers and computer scientists.
\Textcite{vanKreveld2001} proposed five gradual changes
to support the continuous zooming of maps, 
which are \emph{moving}, \emph{rotating}, \emph{morphing}, 
\emph{fading}, and \emph{appearing}. 
He suggested using these gradual changes 
to adapt discrete generalization operators for CMG.
\textcite{Sester2005_CG} suggested simplifying building
footprints based on small incremental steps and 
to animate each step smoothly.
\textcite{Li2012Continuous} built hierarchies of road segments,
which they then used to omit road segments 
from lower levels of the hierarchy.
Moreover, they evaluated similarities 
between their results and existing maps.
\textcite{Peng2017Building} gradually grew
buildings to built-up areas by aggregating buildings 
whenever they become too close.
\textcite{Touya2017Progressive} progressively replaced
buildings with blocks. 
In addition, their method automatically inferred landmarks 
and put the landmarks on top of the blocks.
\textcite{Suba2016Road} continuously generalized road networks
which are represented as a set of areas.
Their method repeatedly finds the least-important area 
and then either merges it with an adjacent area 
or collapses it to a line segment.
\textcite{Danciger2009} investigated the growing of regions, 
while preserving topology, area ratios, and
relative positions.
The strategy of using two maps at different scales
to generate intermediate-scale maps has been studied in multiple
representations, e.g., with respect to the selection of roads or
rivers~\parencite{Peng2012River,Girres2014}. 
Actually, this strategy is the key idea of the
morphing-based methods for CMG.
In order to morph from one polyline to another polyline,
which respectively represent, say, roads on a larger-scale map 
and a smaller-scale map, we first need to compute 
corresponding points between them 
\parencite[e.g.,][]{Cecconi2003,Noellenburg2008,Chazal2010BallMap,
Deng2015,Li2017_Building,Li2017Annealing}.
Then morphing can be realized by interpolating a set of 
intermediate polylines.
% Among the methods of computing corresponding points,
\textcite{Noellenburg2008} computed an optimum
correspondence between two given polylines 
according to some cost function.
While straight-line trajectories 
are often used for interpolation
\parencite[e.g.,][]{Cecconi2003,Deng2015},
\textcite{Whited2011BallMorph} considered four other alternatives, 
i.e., \emph{hat}, \emph{tangent}, \emph{circular}, 
and \emph{parabolic} paths
based on so-called \emph{ball-map}
\parencite{Chazal2010BallMap}.
\textcite{Peng2013LSA} defined trajectories requiring that
angles in vertices and edge lengths should change linearly.
As these requirements may not agree with each other,
their method mediates between them using 
least-squares adjustments.
\textcite{Peng2016Admin} morphed county boundaries
to provincial boundaries.
For county boundaries that do not have corresponding 
provincial boundaries, they generated the correspondences based 
on \emph{compatible triangulations}.
\Textcite{vanOosterom2014tGAP} used
a data structure called
\emph{smooth topological generalized area partitioning}
to support visualizing CMG.
One of their contributions is that
a polygon is merged into another polygon continuously
by moving the boundary of the former.
\textcite{Huang2017Matrix} proposed a matrix-based structure 
to support CMG,
using a river network as an example.
For a given scale, 
their structure yields the rivers that should be kept 
as well as how much these rivers should be simplified.

\mypar{Optimization in map generalization}
Map generalization generally specifies 
and takes into account requirements
in order to produce maps of high quality
\parencite{Stoter2009Requirements}.
We categorize requirements as hard and soft constraints.
For example, when users zoom out, 
some land-cover areas become too small to be seen.
These areas need to be aggregated.
When we aggregate one area into another, 
the type of the former is changed to the type of the latter. 
In this problem, a hard constraint could be that 
we aggregate only two polygons at each step 
in order to keep changes small
(see for example \fig\ref{fig:AreaAgg_example}). 
A soft constraint could be that 
we wish to minimize the changes of types, e.g., 
we prefer aggregating a grass area into a farm area 
rather than into a settlement area.
This is a typical \emph{optimization} problem,
where we stick to hard constraints and 
try to fulfill soft ones as well as possible.
Optimization for map generalization is important 
not only because it finds optimal solutions,
but also because it helps us to evaluate the quality of a model
\parencite{Haunert2017Label,
Haunert2008Assuring,Haunert2016Optimization}.
Recall that we wish to minimize the changes of types
when aggregating areas one by one.
A model could be to minimize 
the \emph{greatest} change over all the steps.
Using optimization, we are able to find optimal solutions
of this model at least for small instances.
If even the optimal solutions are bad,
then the model may be not reasonable.
In this case, we should improve the model; 
we may want to minimize 
the \emph{average} change over all the steps.
Moreover, optimization is useful for evaluating heuristics.
We need heuristics because
many optimization problems cannot be solved efficiently
\parencite[e.g.,][]{HaunertWolff2010AreaAgg,Haunert2016Partition}.
While heuristics can find some solutions in reasonable time,
it is important to know the quality of 
these solutions.
Fortunately, we can often find an optimal solution when 
the size of an instance is sufficiently small.
Consequently, we are able to evaluate 
the quality of a heuristic 
by comparing its results with optimal solutions
on small instances.

\begin{figure}[tb]
\centering
\includegraphics{AreaAgg_example}
\caption{The input and a possible output 
	for an instance of 	our problem}
\label{fig:AreaAgg_example}
\end{figure}

\mypar{Optimization in \emph{continuous} map generalization}
Optimization becomes more delicate
when we deal with CMG.
In this field, we have requirements 
not only for a specific map
but also for relations between maps at difference scales. 
%
Some optimization techniques have been applied to CMG.
In the aforementioned article,
\textcite{Noellenburg2008} used dynamic programming
to match points of two polylines to support morphing
according to some matching cost.
\textcite{sahw-oarps-ICAGW13} used 
mixed-integer linear programming 
to select points of interest.
They required that a point, once disappeared, 
should not show up again during zooming out. 
They also required that any two points should be 
sufficiently far away from each other.
Based on these requirements, 
they wanted to show as many points as possible 
for a given scale interval.
\textcite{Chimani2014Eat} computed a deletion sequence
for a road network by integer linear programming
and efficient approximation algorithms.
They wanted to delete a stroke, 
which is a sequence of edges, at each step
while keeping the remaining network connected.
They assigned each edge a weight, 
and their objective was to maximize the total weight 
over all the road networks of all the steps.
\textcite{Peng2013LSA} defined trajectories 
based on LSA for morphing between polylines, 
where LSA is used to mediate between the requirements 
for angles and edge lengths of the intermediate polylines.

\mypar{Problem definition}
The land-cover area is of significant importance on maps.
When users zoom out, some land-cover areas become
too tiny to be seen, which result in visual clutter.
In order to provide users 
with good visual experience during zooming operations,
we propose to remove these tiny areas.
We plan to achieve this goal by 
aggregating them into neighboring land-cover areas.
A \emph{land-cover map} is a planar subdivision in which 
each area belongs to a land-cover class or \emph{type}.
Suppose that there are two land-cover maps of different scales 
that cover the same spatial region.
We consider the problem of finding a sequence 
of small incremental changes that gradually transforms 
the larger-scale map (the \emph{start map}) to 
the smaller-scale map (the \emph{goal map}).
We use this sequence to generate and show land-cover maps at 
intermediate scales (see \fig\ref{fig:AreaAgg_example}).
In this way, we try to avoid large and discrete changes
during zooming.

@@

\mypar{Contribution}
We formally define our problem, 
introduce the basic concepts of our method, 
and analyze the size of our model in a worst-case scenario
(\sect\ref{sec:AreaAgg_Preliminaries}).
We prove that our problem is NP-hard
(\sect\ref{sec:AreaAgg_NP-hardness}).
We define our cost functions in 
\sect\ref{sec:AreaAgg_CostFunctions}.
Then, we compare three methods for finding aggregation sequences.
First, we develop 
a greedy algorithm (\sect\ref{sec:AreaAgg_Greedy}).
Second, we present a new global optimization approach
based on the \Astar algorithm 
(\sect\ref{sec:AreaAgg_AStar}).
Third, we model our pathfinding problem as
an \emph{integer linear program} (ILP), 
and then we solve this program with minimizing our cost function.
Our ILP uses binary (0--1) variables. 
These variables help us to model our problem, 
but in general, it is NP-hard 
to solve an ILP optimally.
By comparing with the greedy algorithm, 
which is used as a benchmark,
we are able to see whether it is worth 
to use \Astar or the ILP-based algorithm, 
which are more complex and slower.  
Our case study 
uses a dataset of the German topographic database ATKIS 
(\sect\ref{sec:AreaAgg_CaseStudy}).
In the conclusions, we show possible ways to improve our 
methods in \sect\ref{sec:AreaAgg_Conclusions}.

@@

@@

To find a sequence of small changes 
that transforms the start map into the goal map,
we require that 
every change involves only two areas of the current map.
More precisely, in each step the smallest area~$u$ is merged 
with one of its neighbors (adjacent areas)~$v$
such that~$u$ and~$v$ are replaced by their union.
The type of the union is restricted to be 
the type of either~$u$ or~$v$.
If the union uses the type of~$u$, 
we say that area~$v$ is \emph{aggregated into} area~$u$, 
and vice versa. 
How to aggregate exactly is decided by 
optimizing a global cost function.
This requirement ensures that the 
size of the smallest area on the map increases in each step.
Hence, the sequence reflects a gradual reduction of the 
map's scale.
From another perspective, 
we consider the smallest area as the least important, 
rather than involving more rules for (non-)importance. 
Even though the requirement reduces 
the number of possible solutions,
there is still enough room for optimization 
since we leave open with
which of its neighbors the smallest area is aggregated.
We term a sequence of changes 
that adheres to our smallest-first requirement simply 
an \emph{aggregation sequence}.

@@

Although we have shown that the graph of subdivisions
has an exponential size,
one may develop a clever algorithm 
to find an optimal sequence efficiently.
In the following, we prove that 
finding such a sequence is indeed NP-hard.
In the proof, we neglect the cost of compactness or the cost of length.
Considering one of the two costs 
will make the finding even more difficult.

\begin{proof}
Our NP-hardness proof is by reduction from 
the NP-complete problem \textsc{PlanarVertexCover}, 
which is to decide, for a given 
planar graph~$G_\mathrm{A} = (V_\mathrm{A},E_\mathrm{A})$, 
whether there exists a vertex cover 
with at most a given number~$k_\mathrm{A}$ of vertices. 
For an instance of \textsc{PlanarVertexCover}
(\fig\ref{fig:AreaAgg_Reduction}a), 
we define a corresponding instance of \textsc{AreaAggregationSequence}
whose start map consists of red, black, and white areas and 
whose goal map consists of only one large red patch.
The adjacency graphs of the two maps are illustrated 
in \figs\ref{fig:AreaAgg_Reduction}b and~\ref{fig:AreaAgg_Reduction}c, 
where the colors of the vertices represent 
the colors of the corresponding areas.
More precisely, for each vertex of~$G_\mathrm{A}$
in \fig\ref{fig:AreaAgg_Reduction}a, 
we define a red vertex and a black vertex, 
which we connect with an edge. 
For each edge of~$G_\mathrm{A}$, 
we define two white vertices and 
connect them with the two black vertices
(\fig\ref{fig:AreaAgg_Reduction}b).

We define the weights of the vertices 
in \fig\ref{fig:AreaAgg_Reduction}b as follows:
\begin{itemize}
\item Every white vertex has weight~$1$.
\item Every black vertex has weight~$2$.
\item Every red vertex has weight~$2|V_\mathrm{A}| + 2|E_\mathrm{A}|$,
which is equal to the total weight of all white and black vertices.
\end{itemize}
Since in each aggregation step, 
we require the smallest area to be aggregated with one of its neighbors, 
our definition of the weights to a certain degree determines 
the order in which the vertices are selected:
\begin{itemize}
\item \emph{Phase I}: In each of the first~$2|E_\mathrm{A}|$ steps, 
a white vertex is selected and merged with one of its neighbors, 
such that the white vertex receives the neighbor's color or vice versa.
\item \emph{Phase II}: In each of the next~$|V_\mathrm{A}|$ steps, 
a non-red vertex is selected and merged with one of its neighbors.
\item \emph{Phase III}: $|V_\mathrm{A}|-1$ steps remain to reach the goal map.
\end{itemize}

To complete the reduction, 
we need to define the costs of color changes. 
For any color change, 
we charge one unit of cost per unit weight.
Due to our construction, Phases II and III can be accomplished with
a total cost of~$2|V_\mathrm{A}|+2|E_\mathrm{A}|$, 
no matter how Phase I is accomplished.
This is because, after Phase I, 
every non-red patch will be adjacent to a red patch (vertex).
Thus, if any non-red patch becomes selected in Phase II, 
it can aggregate with a red patch (vertex) and 
receive the color red. 
This implies that Phase II costs $2|V_\mathrm{A}|+2|E_\mathrm{A}|$ 
(which is equal to the total weight of 
all initially white and black vertices) and, 
since after Phase II all patches are red, 
Phase III does not cause any additional cost.  
It is also clear that 
there is no cheaper way to accomplish Phases II and III,
since it is impossible to color a vertex red in Phase I.
Consequently, since the total cost of Phases II and III is fixed, 
it is only interesting to ask 
at which cost Phase I can be accomplished.
It turns out that, if $G_\mathrm{A}$ 
has a vertex cover $C_\mathrm{A} \subseteq V_\mathrm{A}$, 
then Phase I can be accomplished with cost $2|C_\mathrm{A}|$;
only the black vertices corresponding to vertices in~$C_\mathrm{A}$ 
need to change their color from black to white, and 
each of them has weight~$2$ (see \fig\ref{fig:reduction2}).
To summarize, if graph~$G_\mathrm{A}$ has a vertex cover~$C_\mathrm{A}$, 
then the corresponding instance of \textsc{AreaAggregationSequence} 
has a solution of 
total cost~$2|C_\mathrm{A}|+2|V_\mathrm{A}|+2|E_\mathrm{A}|$.

@@

It is difficult to define what \emph{reasonable} exactly means 
because users may have different preferences.
Four preferences have been discussed by
\textcite{Cheng2006}; see \fig\ref{fig:AreaAgg_Preferences}.
A small land-cover area can be aggregated into another area 
that isolates the area 
(\fig\ref{fig:AreaAgg_Preferences}b), 
that is the largest neighbor 
(\fig\ref{fig:AreaAgg_Preferences}c), 
that shares the longest boundary 
(\fig\ref{fig:AreaAgg_Preferences}d), or 
that has the most similar type
(\fig\ref{fig:AreaAgg_Preferences}e).
To keep our aggregation problem independent of user preferences,
our cost function takes two aspects into account: 
one based on semantics and 
the other based on shape.
%
In terms of semantics, we require that 
the \emph{type} of a land-cover area changes 
as little as possible.
This requirement means that we prefer, for example, 
aggregating an area with type \emph{swamp} 
into an area with type \emph{wet ground} 
rather than into an area with type \emph{city}.
%
In terms of shape, we hope to have areas 
which are as \emph{compact} as possible.
Our argument is that an area is easier 
to be identified by a human being 
if it is more compact (less clutter).
%
We also consider the total \emph{length} 
of the interior boundaries as an alternative compactness;
we consider subdivision~\Pnode 
as more compact than subdivision~$P_{t,i'}$ 
if the total length of the interior boundaries of~\Pnode 
is less than that of~$P_{t,i'}$.
We add this alternative because we want to make a comparison 
involving an ILP, 
where a \emph{linear} cost function must be used.
Note that most compactness measures
are \emph{not} linear;
for example, see \textcite{Maceachren1985,Li2013Compactness}.
Although the length of interior boundaries 
is not sufficiently precise 
to describe compactness \parencite{Young1988},
it is often used as a fair alternative
when compactness is considered in an ILP
\parencite[e.g.,][]{Minas2016,Wright1983}.
\textcite{HaunertWolff2010AreaAgg} employed 
the centroids of a set of land-cover areas.
One of their costs is the sum of the distances 
from the centroids to a \emph{reference point}.
The reference point is one of the centroids
that minimizes the sum.
The sum of the distances can be computed linearly.
We use the length of interior boundaries 
instead of the distance of centroids because the former 
is more relevant to the shapes of the patches.
Also, \textcite{Harrie2015Readability} showed that
longer lines generally yield lower map readability.

@@

We use the compactness definition of \citet{Frolov1975}, 
i.e., the compactness value for a patch, say,~$u$ is
\begin{equation*}
\label{eq:comp}
c(u)=\frac{2 \sqrt{\pi A_u}}{l_u},
\end{equation*}
where~$A_u$ and~$l_u$ are 
the area and the perimeter. 
For a subdivision \Psnode, we denote by~$C(\Psnode)$ 
the set of the patches' compactnesses.

@@

\subsection{Combining cost functions}
\label{sec:AreaAgg_Combining}
In order to minimize the type change 
and maximize the compactness,
we combine the two cost functions as
\begin{equation}
\label{eq:g_1}
g_1(\Pistar)= (1-\lambda)g_\mathrm{type}(\Pistar)
+\lambda g_\mathrm{comp}(\Pistar),
\end{equation}
where~$\lambda \in [0,1]$ is a parameter 
to assign importances 
of~$f_\mathrm{type}$ and~$f_\mathrm{comp}$.
We simply use~$\lambda=0.5$ in our experiments. 
We want to find a path~$\Pi$ from~$\Pstart$ to~$\Pnode$ 
that minimizes, among all such paths,~$g_1(\Pistar)$.
Slightly abusing notation, we denote the cost of
an optimal path from~${P}_{\mathrm{start}}$ to~\Pnode 
by~$g_1(\Pnode)$.
Using $g_1(\Pnode)$, we compare a greedy algorithm and \Astar
in finding optimal sequences for area aggregation.

As said before, we want to make a comparison involving
integer linear programming.
Therefore, we also introduce a combination
that can be computed linearly. That is,
\begin{equation}
\label{eq:g_2}
g_2(\Pistar)= (1-\lambda)g_\mathrm{type}(\Pistar)
+\lambda g_\mathrm{lgth}(\Pistar).
\end{equation}
We compare the greedy algorithm, \Astar, and an ILP-based 
algorithm using $g_2$.

>>>>

In each step of the sequence that we compute, 
the smallest area is merged with one of its neighbors. 
We do not select that neighbor according to a prescribed rule 
but compute the whole sequence of pairwise merges at once, 
based on global optimization.
We have proved that this problem is NP-hard.
We formalize this optimization problem as that of 
finding a shortest path in a (very large) graph.
We present the \Astar algorithm and integer linear programming
to solve this optimization problem.
To avoid long computing times, we allow the two methods to 
return non-optimal results.
In addition, we present a greedy algorithm as a benchmark.
We tested the three methods with a
dataset of the official German topographic database ATKIS.
Our main result is that
\Astar finds optimal aggregation sequences for more instances 
than the other two methods
within a given time frame.
%
%
\end{abstract}

@@

In our digital age, people interactively read maps 
on computers and mobile phones.
An often used interaction is zooming. 
When users zoom in or out, 
a map must be changed to provide information 
appropriate to the corresponding zoom level.
However, large discrete changes may distract users.
The \emph{on-the-fly generalization}~\parencite{Weibel2017Fly},
which generalizes features in real time, can mitigate this problem.
Still, large discrete changes can be introduced.
By a usability test, \textcite{Midtbo2007} have shown that 
a map is easier to follow 
if the map extent transits smoothly than stepwise. 
In addition to smoothly transiting map extent, 
we want to change also map features smoothly 
when users are zooming.
we believe that this strategy will allow users 
to follow maps even more easily.
The process of producing maps at any different scales
with smooth changes 
is known as \emph{continuous map generalization} (CMG), 
or simply \emph{continuous generalization}.
Ideally, there should be no discrete change in CMG.
However, the term is also used when 
the discrete changes are small enough not to be noticed as,
e.g., \textcite{Suba2016Road} state.
We believe that digital maps will eventually 
achieve smooth changes for zooming,
and CMG is an effective way to realize smooth changes.

\mypar{Problem definition}
In this paper, we deal with CMG of land-cover areas.
The land-cover area is of significant importance on maps.
When users zoom out, some land-cover areas become
too tiny to be seen, which result in visual clutter.
In order to provide users 
with good visual experience during zooming operations,
we propose to remove these tiny areas.
We plan to achieve this goal by 
aggregating them into neighboring land-cover areas.
A \emph{land-cover map} is a planar subdivision in which 
each area belongs to a land-cover class or \emph{type}.
Suppose that there are two land-cover maps of different scales 
that cover the same spatial region.
We consider the problem of finding a sequence 
of small incremental changes that gradually transforms 
the larger-scale map (the \emph{start map}) to 
the smaller-scale map (the \emph{goal map}).
We use this sequence to generate and show land-cover maps at 
intermediate scales (see \fig\ref{fig:AreaAgg_example}).
In this way, we try to avoid large and discrete changes
during zooming.

\begin{figure}[tb]
\centering
\includegraphics{AreaAgg_example}
\caption{The input and a possible output of an aggregation sequence 
	for an instance of our problem}
\label{fig:AreaAgg_example}
\end{figure}

@@

\mypar{Contribution}
We formally define our problem, 
introduce the basic concepts of our method, 
and analyze the size of our model in a worst-case scenario
(\sect\ref{sec:AreaAgg_Preliminaries}).
We define our cost functions in 
\sect\ref{sec:AreaAgg_CostFunctions}.
We prove that our problem is NP-hard
(\sect\ref{sec:AreaAgg_NP-hardness}).
Then, we develop and compare three methods 
for finding aggregation sequences.
First, we present 
a greedy algorithm (\sect\ref{sec:AreaAgg_Greedy}).
Second, we develop a new global optimization approach
based on the \Astar algorithm 
(\sect\ref{sec:AreaAgg_AStar}).
Third, we model our pathfinding problem as
an \emph{integer linear program} (ILP), 
and then we solve this program with minimizing our cost function.
Our ILP uses binary (0--1) variables. 
These variables help us to model our problem, 
but in general, it is NP-hard 
to solve an ILP optimally.
By comparing with the greedy algorithm, 
which is used as a benchmark,
we are able to see whether it is worth 
to use \Astar or the ILP-based algorithm, 
which are more complex and slower.  
Our case study 
uses a dataset of the German topographic database ATKIS 
(\sect\ref{sec:AreaAgg_CaseStudy}).
In the conclusions, we show possible ways to improve our 
methods in \sect\ref{sec:AreaAgg_Conclusions}.

@@

\section{Related Work}

\subsection{Continuous map generalization}

\emph{Continuous map generalization} (CMG)
has received a lot of attention
from cartographers and computer scientists.
\Textcite{vanKreveld2001} proposed five gradual changes
to support the continuous zooming of maps, 
which are \emph{moving}, \emph{rotating}, \emph{morphing}, 
\emph{fading}, and \emph{appearing}. 
He suggested using these gradual changes 
to adapt discrete generalization operators for CMG.
\textcite{Sester2005_CG} suggested simplifying building
footprints based on small incremental steps and 
to animate each step smoothly.
\textcite{Li2012Continuous} built hierarchies of road segments,
which they then used to omit road segments 
from lower levels of the hierarchy.
Moreover, they evaluated similarities 
between their results and existing maps.
\textcite{Peng2017Building} gradually grew
buildings to built-up areas by aggregating buildings 
whenever they become too close.
\textcite{Touya2017Progressive} progressively replaced
buildings with blocks. 
In addition, their method automatically inferred landmarks 
and put the landmarks on top of the blocks.
\textcite{Suba2016Road} continuously generalized road networks
which are represented as a set of areas.
Their method repeatedly finds the least-important area 
and then either merges it with an adjacent area 
or collapses it to a line segment.
\textcite{Danciger2009} investigated the growing of regions, 
while preserving topology, area ratios, and
relative positions.
The strategy of using two maps at different scales
to generate intermediate-scale maps has been studied in multiple
representations, e.g., with respect to the selection of roads or
rivers~\parencite{Peng2012River,Girres2014}. 
Actually, this strategy is the key idea of the
morphing-based methods for CMG.
In order to morph from one polyline to another polyline,
which respectively represent, say, roads on a larger-scale map 
and a smaller-scale map, we first need to compute 
corresponding points between them 
\parencite[e.g.,][]{Cecconi2003,Noellenburg2008,Chazal2010BallMap,
Deng2015,Li2017_Building,Li2017Annealing}.
Then morphing can be realized by interpolating a set of 
intermediate polylines.
% Among the methods of computing corresponding points,
\textcite{Noellenburg2008} computed an optimum
correspondence between two given polylines 
according to some cost function.
While straight-line trajectories 
are often used for interpolation
\parencite[e.g.,][]{Cecconi2003,Deng2015},
\textcite{Whited2011BallMorph} considered four other alternatives, 
i.e., \emph{hat}, \emph{tangent}, \emph{circular}, 
and \emph{parabolic} paths
based on so-called \emph{ball-map}
\parencite{Chazal2010BallMap}.
\textcite{Peng2013LSA} defined trajectories requiring that
angles in vertices and edge lengths should change linearly.
As these requirements may not agree with each other,
their method mediates between them using 
least-squares adjustments.
\textcite{Peng2016Admin} morphed county boundaries
to provincial boundaries.
For county boundaries that do not have corresponding 
provincial boundaries, they generated the correspondences based 
on \emph{compatible triangulations}.
\Textcite{vanOosterom2014tGAP} used
a data structure called
\emph{smooth topological generalized area partitioning}
to support visualizing CMG.
One of their contributions is that
a polygon is merged into another polygon continuously
by moving the boundary of the former.
\textcite{Huang2017Matrix} proposed a matrix-based structure 
to support CMG,
using a river network as an example.
For a given scale, 
their structure yields the rivers that should be kept 
as well as how much these rivers should be simplified.

\subsection{Optimization in map generalization}

Map generalization generally specifies 
and takes into account requirements
in order to produce maps of high quality
\parencite{Stoter2009Requirements}.
We categorize requirements as hard and soft constraints.
For example, when users zoom out, 
some land-cover areas become too small to be seen.
These areas need to be aggregated.
When we aggregate one area into another, 
the type of the former is changed to the type of the latter. 
In this problem, a hard constraint could be that 
we aggregate only two polygons at each step 
in order to keep changes small
(see for example \fig\ref{fig:AreaAgg_example}). 
A soft constraint could be that 
we wish to minimize the changes of types, e.g., 
we prefer aggregating a grass area into a farm area 
rather than into a settlement area.
This is a typical \emph{optimization} problem,
where we stick to hard constraints and 
try to fulfill soft ones as well as possible.
Optimization for map generalization is important 
not only because it finds optimal solutions,
but also because it helps us to evaluate the quality of a model
\parencite{Haunert2017Label,
Haunert2008Assuring,Haunert2016Optimization}.
Recall that we wish to minimize the changes of types
when aggregating areas one by one.
A model could be to minimize 
the \emph{greatest} change over all the steps.
Using optimization, we are able to find optimal solutions
of this model at least for small instances.
If even the optimal solutions are bad,
then the model may be not reasonable.
In this case, we should improve the model; 
we may want to minimize 
the \emph{average} change over all the steps.
Moreover, optimization is useful for evaluating heuristics.
We need heuristics because
many optimization problems cannot be solved efficiently
\parencite[e.g.,][]{HaunertWolff2010AreaAgg,Haunert2016Partition}.
While heuristics can find some solutions in reasonable time,
it is important to know the quality of 
these solutions.
Fortunately, we can often find an optimal solution when 
the size of an instance is sufficiently small.
Consequently, we are able to evaluate 
the quality of a heuristic 
by comparing its results with optimal solutions
on small instances.

\subsection{Optimization in \emph{continuous} map generalization}

Optimization becomes more delicate
when we deal with CMG.
In this field, we have requirements 
not only for a specific map
but also for relations between maps at difference scales. 
%
Some optimization techniques have been applied to CMG.
In the aforementioned article,
\textcite{Noellenburg2008} used dynamic programming
to match points of two polylines to support morphing
according to some matching cost.
\textcite{sahw-oarps-ICAGW13} used 
mixed-integer linear programming 
to select points of interest.
They required that a point, once disappeared, 
should not show up again during zooming out. 
They also required that any two points should be 
sufficiently far away from each other.
Based on these requirements, 
they wanted to show as many points as possible 
for a given scale interval.
\textcite{Chimani2014Eat} computed a deletion sequence
for a road network by integer linear programming
and efficient approximation algorithms.
They wanted to delete a stroke, 
which is a sequence of edges, at each step
while keeping the remaining network connected.
They assigned each edge a weight, 
and their objective was to maximize the total weight 
over all the road networks of all the steps.
\textcite{Peng2013LSA} defined trajectories 
based on LSA for morphing between polylines, 
where LSA is used to mediate between the requirements 
for angles and edge lengths of the intermediate polylines.

@@

To find a sequence of small changes 
that transforms the start map into the goal map,
we require that 
every change involves only two areas of the current map.
More precisely, in each step the smallest area~$u$ is merged 
with one of its neighbors~$v$ 
($v$ does not have to be the smallest neighbor)
such that~$u$ and~$v$ are replaced by their union.
The type of the union is restricted to be 
the type of either~$u$ or~$v$.
If the union uses the type of~$u$, 
we say that area~$v$ is \emph{aggregated into} area~$u$, 
and vice versa. 
How to aggregate exactly is decided by 
optimizing a global cost function.
This requirement ensures that the 
size of the smallest area on the map increases in each step.
Hence, the sequence reflects a gradual reduction of the 
map's scale.
From another perspective, 
we consider the smallest area as the least important, 
rather than involving more rules for (non-)importance. 
Even though the requirement reduces 
the number of possible solutions,
there is still enough room for optimization 
since we leave open with
which of its neighbors the smallest area is aggregated.
We term a sequence of changes 
that adheres to our smallest-first requirement simply 
an \emph{aggregation sequence}.

@@

@@

It is difficult to define what \emph{reasonable} exactly means 
because users may have different preferences.
Four preferences have been discussed by
\textcite{Cheng2006}; see \fig\ref{fig:AreaAgg_Preferences}.
A small land-cover area can be aggregated into another area 
that isolates the area 
(\fig\ref{fig:AreaAgg_Preferences}b), 
that is the largest neighbor 
(\fig\ref{fig:AreaAgg_Preferences}c), 
that shares the longest boundary 
(\fig\ref{fig:AreaAgg_Preferences}d), or 
that has the most similar type
(\fig\ref{fig:AreaAgg_Preferences}e).
To keep our aggregation problem independent of user preferences,
our cost function takes two aspects into account: 
one based on semantics and 
the other based on shape.
%
In terms of semantics, we require that 
the \emph{type} of a land-cover area changes 
as little as possible.
This requirement means that we prefer, for example, 
aggregating an area with type \emph{swamp} 
into an area with type \emph{wet ground} 
rather than into an area with type \emph{city}.
%
In terms of shape, we hope to have areas 
which are as \emph{compact} as possible.
Our argument is that an area is easier 
to be identified by a human being 
if it is more compact (less clutter).
In this paper, we ignore the fact that
some features may inherently take linear forms
(e.g., rivers).
%
We also consider the total \emph{length} 
of the interior boundaries as an alternative compactness;
we consider subdivision~\Pnode 
as more compact than subdivision~$P_{t,i'}$ 
if the total length of the interior boundaries of~\Pnode 
is less than that of~$P_{t,i'}$.
We add this alternative because we want to make a comparison 
involving an ILP, 
where a \emph{linear} cost function must be used.
Note that most compactness measures
are \emph{not} linear;
for example, see \textcite{Maceachren1985,Li2013Compactness}.
Although the length of interior boundaries 
is not sufficiently precise 
to describe compactness \parencite{Young1988},
it is often used as a fair alternative
when compactness is considered in an ILP
\parencite[e.g.,][]{Minas2016,Wright1983}.
\textcite{HaunertWolff2010AreaAgg} employed 
the centroids of a set of land-cover areas.
One of their costs is the sum of the distances 
from the centroids to a \emph{reference point}.
The reference point is one of the centroids
that minimizes the sum.
The sum of the distances can be computed linearly.
We use the length of interior boundaries 
instead of the distance of centroids because the former 
is more relevant to the shapes of the patches.
Also, \textcite{Harrie2015Readability} showed that
longer lines generally yield lower map readability.

@@

We use the compactness definition of \citet{Frolov1975}, 
i.e., the compactness value for a patch, say,~$u$ is
\begin{equation}
\label{eq:comp}
c(u)=\frac{2 \sqrt{\pi A_u}}{l_u},
\end{equation}
where~$A_u$ and~$l_u$ are 
the area and the perimeter. 
For a subdivision \Psnode, we denote by~$C(\Psnode)$ 
the set of the patches' compactnesses.

@@

\subsection{Combining cost functions}
\label{sec:AreaAgg_Combining}

When we generate a sequence of intermediate-scale maps,
we want to change the types of the land-cover areas 
as little as possible
and want to have compact land-cover areas.
Therefore, we combine 
the cost of type change (\eq\ref{eq:g_type})
and the cost of compactness (\eq\ref{eq:g_comp}).
That is,
\begin{equation}
\label{eq:g_1}
g_1(\Pistar)= (1-\lambda)g_\mathrm{type}(\Pistar)
+\lambda g_\mathrm{comp}(\Pistar),
\end{equation}
where~$\lambda \in [0,1]$ is a parameter 
to assign importances 
of~$f_\mathrm{type}$ and~$f_\mathrm{comp}$.
We simply use~$\lambda=0.5$ in our experiments. 
We want to find a path~$\Pi$ from~$\Pstart$ to~$\Pnode$ 
that minimizes, among all such paths,~$g_1(\Pistar)$.
Slightly abusing notation, we denote the cost of
an optimal path from~${P}_{\mathrm{start}}$ to~\Pnode 
by~$g_1(\Pnode)$.
Using $g_1(\Pnode)$, we compare a greedy algorithm and \Astar
in finding optimal sequences for area aggregation.

As said before, we want to make a comparison involving
integer linear programming 
while our cost of compactness (see \eq\ref{eq:comp})
cannot be computed linearly in an integer linear program.
Therefore, we combine 
the cost of type change (\eq\ref{eq:g_type})
and the cost of length (\eq\ref{eq:g_length}),
which can be computed linearly in an integer linear program. 
That is,
\begin{equation}
\label{eq:g_2}
g_2(\Pistar)= (1-\lambda)g_\mathrm{type}(\Pistar)
+\lambda g_\mathrm{lgth}(\Pistar).
\end{equation}
We compare the greedy algorithm, \Astar, and an ILP-based 
algorithm using~$g_2$.
